%-------------------------
% Resume in Latex
% Author : Yousef Mardrosyan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yousef Mardrosyan} \\ \vspace{1pt}
    \small (248)-808-0446 $|$ \href{mailto:yousefm2787@gmail.com}{\underline{yousefm2787@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/yousef-mardrosyan-3b38b4268/}{\underline{linkedin.com/in/yousef-mardrosyan-3b38b4268}} $|$
    \href{https://github.com/azvali}{\underline{github.com/azvali}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oakland University}{Rochester Hills, MI}
      {Bachelor of Science in Computer Science}{Dec 2024}
      \resumeItemListStart
        \resumeItem{GPA: 3.61/4.0}
        \resumeItem{Dean's List: Fall 2021 – Fall 2024}
      \resumeItemListEnd
    \textbf{Citizenship:} U.S. Citizen; eligible for DoD Secret Clearance
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{June 2024 – Aug 2024}
      {Department of Homeland Security}{}
      \resumeItemListStart
        \resumeItem{Redesigned the Chief of Staff's landing page (serving \textbf{60,000+} daily users), improving UI/UX and ensuring Section 508 compliance.}
        \resumeItem{Contributed to Agile sprints by delivering wireframes in Figma and implementing iterative user feedback.}
        \resumeItem{Assisted with internal tooling using Git and Confluence for version control and documentation.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{May 2023 – June 2024}
      {Oakland University}{Rochester Hills, MI}
      \resumeItemListStart
        \resumeItem{Created a Python script to auto-generate UML diagrams for \textbf{50+} student projects, saving \textbf{20+} hours/semester.}
        \resumeItem{Partnered with \textbf{5} PhD students to discover and document vulnerabilities in PyTorch and TensorFlow.}
        \resumeItem{Utilized JIRA and Git for version control and collaborative research workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant, Computer Science}{Jan 2024 – May 2024}
      {Oakland University}{Rochester Hills, MI}
      \resumeItemListStart
        \resumeItem{Co-taught C\# fundamentals to \textbf{60+} students, helping improve average exam scores by \textbf{15\%}.}
        \resumeItem{Held weekly office hours, assisting \textbf{20+} students with debugging and algorithmic concepts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Vendora} $|$ \emph{React, C\#, ASP.NET Core, PostgreSQL} $|$ \href{https://github.com/azvali/Vendora}{\underline{GitHub}}}{} 
      \resumeItemListStart
        \resumeItem{Built a full-stack e-commerce platform with user accounts, product listings, image uploads, and browsing.}
        \resumeItem{Developed a secure C\# backend (ASP.NET Core) with JWT auth and API responses optimized for \textbf{$<$200ms}.}
        \resumeItem{Designed RESTful APIs using PostgreSQL (Npgsql) and OOP for a modular, maintainable data layer.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Whisp} $|$ \emph{React, Flask, PostgreSQL, Socket.IO} $|$ \href{https://github.com/azvali/Whisp}{\underline{GitHub}}}{}
      \resumeItemListStart
        \resumeItem{Engineered a real-time chat app (Socket.IO) with an average message latency under \textbf{100ms}.}
        \resumeItem{Implemented secure user authentication with JWT, password hashing, and account recovery.}
        \resumeItem{Created a Flask RESTful API for user, message, and friend management.}
        \resumeItem{Developed a React front-end for login, chat, and contact features.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Fooducate} $|$ \emph{React, Firebase, OpenAI API, Node.js} $|$ \href{https://github.com/azvali/Fooducate2}{\underline{GitHub}}}{}
      \resumeItemListStart
        \resumeItem{Built a mobile nutrition app to analyze food images for nutritional data.}
        \resumeItem{Integrated an AI diet coach (OpenAI API) providing personalized meal suggestions in under \textbf{2s}.}
        \resumeItem{Used Firebase for secure authentication and real-time calorie tracking.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \small{
    \textbf{Languages:} C\#, Python, JavaScript (ES6+), SQL, C++ \\
    \textbf{Backend:} ASP.NET Core, Flask, Node.js, REST API Development, JWT Authentication, Socket.IO \\
    \textbf{Frontend:} React, HTML/CSS, Responsive Design, Figma (Wireframing) \\
    \textbf{Databases:} PostgreSQL, Firebase, Npgsql \\
    \textbf{Tools \& Methodologies:} Git, GitHub, JIRA, Confluence, Agile, CI/CD, OOP
  }
\end{itemize}

%-------------------------------------------
\end{document}